---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zenstats

<!-- badges: start -->
[![R-CMD-check](https://github.com/rfsaldanha/zenstats/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/rfsaldanha/zenstats/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

A Zenodo deposit contains some statistics of interest, like the number of views and downloads, that is not available to programmaticaly access through its API. The `zenstats` package scraps deposit webpages and return the deposits statistics as a tibble.

## Installation

You can install the stable release from CRAN.

``` r
install.packages("zenstats")
library(zenstats)
```
Or install the development version of from GitHub:

``` r
# install.packages("remotes")
remotes::install_github("rfsaldanha/zenstats")
library(zenstats)
```

## Example 

```{r example}
library(zenstats)

ids <- c(10036212, 10947952)

deposit_stats(ids, all_versions_only = TRUE, progress = FALSE)
```

## Polite webpage crawling

This package respects the 'robots.txt' policies from Zenodo, including the crawl delay of 10 seconds.

